Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-08-18 docs/00-manuscripts/ieee/performance-best-per-learner.tex
include regr.featureless in benchmark

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method, sorted ascending by RMSE} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR-NRI-VI & SVM & Relief & 28.09 & 18.95 \\ 
  2 & HR & XGBoost & CMIM & 30.88 & 14.47 \\ 
  3 & NRI & Lasso-MBO & No Filter & 31.16 & 15.03 \\ 
  4 & NRI & Ridge-MBO & No Filter & 31.16 & 15.03 \\ 
  5 & HR & RF & Relief & 32.93 & 13.17 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & SVM & Relief & 28.12 & 19.12 \\ 
  2 & NRI & Lasso-MBO & No Filter & 31.16 & 15.03 \\ 
  3 & NRI & Ridge-MBO & No Filter & 31.16 & 15.03 \\ 
  4 & HR & regr.featureless & No Filter & 31.16 & 15.03 \\ 
  5 & HR & RF & Relief & 31.25 & 14.96 \\ 
  6 & HR & XGBoost & Car & 34.07 & 13.57 \\ 
   \hline
\end{tabular}
}
\end{table}
